Models of VOR learning in MHC knockout mice

### 2013-02-12 Notes/VORmodel.tex
Talk about crossovers

First, consider the wild-type, for which $q\pot=q\dep=q$.
Without pre-training:
%
\begin{equation}\label{eq:multiLinWTnopre}
  \Phi = -2\Delta fq\,\frac{M-1}{M},
\end{equation}
%
where it's worth remembering that $\Delta f<0$.
With pre-training:
%
\begin{equation}\label{eq:multiLinWTpre}
\begin{aligned}
  \Phi &= -4\Delta f q \, \frac{(1+2\Delta f)^{M-1} - (1-2\Delta f)^{M-1}}
          {(1+2\Delta f)^M - (1-2\Delta f)^M} \\
       &= -{4\Delta f q}\,\frac{M-1}{M} + \CO(\Delta f)^2.
\end{aligned}
\end{equation}
%

@@

The results of simulations of the two-state model can be seen in \autoref{fig:binary}.
However, this model can be solved exactly:
%
\begin{multline}\label{eq:binarysol}
  \eq = \frac{(f\dep q\dep, f\pot q\pot)}{\lambda},
  \qquad
  \pr(t) = \eq + (\pr(t)-\eq)\e^{-\lambda rt},\\
  \qquad \text{where} \quad
  \lambda = f\pot q\pot + f\dep q\dep.
\end{multline}
%
But it is easier to just substitute $M=2$ into the formulae in \autoref{sec:multistate}.
In this case, the initial rate of change encapsulates the whole solution, as there is only a single exponential decay.

First, consider the wild-type, for which $q\pot=q\dep=q$.
Without pre-training:
%
\begin{equation}\label{eq:binWTnopre}
  \Phi = -\Delta f q,
\end{equation}
%
where, again, it's worth remembering that $\Delta f<0$.
With pre-training:
%
\begin{equation}\label{eq:binWTpre}
\begin{aligned}
  \Phi &= -2\Delta f q.
\end{aligned}
\end{equation}
%
So, we see that pre-training will always speed up learning, unlike what is seen in the experiment.
This can be seen in \autoref{fig:binary}\ref{fig:binary_learnS}.

@@

>>>>

First, consider the wild-type, for which $q\pot=q\dep=q$.
Without pre-training:
%
\begin{equation}\label{eq:multiLinWTnopre}
  \Phi = -2\Delta fq\,\frac{M-1}{M},
\end{equation}
%
where, once more, we should note that $\Delta f<0$.
With pre-training:
%
\begin{equation}\label{eq:multiLinWTpre}
\begin{aligned}
  \Phi &= -4\Delta f q \, \frac{(1+2\Delta f)^{M-1} - (1-2\Delta f)^{M-1}}
          {(1+2\Delta f)^M - (1-2\Delta f)^M} \\
       &= -{4\Delta f q}\,\frac{M-1}{M} + \CO(\Delta f)^2.
\end{aligned}
\end{equation}
%

@@

The results of simulations of the two-state model can be seen in \autoref{fig:binary}.
However, this model can be solved exactly:
%
\begin{multline}\label{eq:binarysol}
  \eq = \frac{(f\dep q\dep, f\pot q\pot)}{\lambda},
  \qquad
  \pr(t) = \eq + (\pr(t)-\eq)\e^{-\lambda rt},\\
  \qquad \text{where} \quad
  \lambda = f\pot q\pot + f\dep q\dep.
\end{multline}
%
But it is easier to just substitute $M=2$ into the formulae in \autoref{sec:multistate}.
In this case, the initial rate of change and the total change encapsulate the whole solution, as there is only a single exponential decay.

First, consider the wild-type, for which $q\pot=q\dep=q$.
Without pre-training:
%
\begin{equation}\label{eq:binWTnopre}
  \Phi = -\Delta f q,
\end{equation}
%
where, once again, it's worth remembering that $\Delta f<0$.
With pre-training:
%
\begin{equation}\label{eq:binWTpre}
\begin{aligned}
  \Phi &= -2\Delta f q.
\end{aligned}
\end{equation}
%
So, we see that pre-training will always speed up learning, unlike what is seen in the experiment.
This can be seen in \autoref{fig:binary}\ref{fig:binary_learnS}.

@@

The only thing we have to worry about is when the wild-type catches up with the mutant.
As the total change will be larger for the wild-type than mutant, it must overtake eventually.
If this happens early enough, the initial period, where the mutant learns faster than wild-type, would not be seen in the experiment.
However, the timescale for this crossover would be similar to the timescale of the exponentials.
In the data, it looks like that timescale is longer than the gaps between successive measurements, so we needn't worry about this.
